The Free-play Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-07 paper.tex
Finished missing bits -- submitted version

Capturing all the interactions taking place during the play sessions is possible
and practical with this setup. Even though the children will typically move a
little, the task is fundamentally a face-to-face, spatially delimited,
interaction, and as such simplifies the data collection. For instance, during
our dataset acquisition campaign (120 children, more than 45h of footage), the
children's faces were automatically detected in 98\% of the recorded frames (see
Section~\ref{sec|dataset}).

@@

\paragraph{Socio-cognitive framing of the task}

\todo{Very much unfinished section.}
focus on abstract socio-cognitive facets (robot
perception and manipulation are simplified); well suited for qualitative and
quantitative analysis using metrics like Słowinski’s Individual Motor Signature
(for behavioural alignment), Anderson's~\cite{anderson2004social} coding of children’s free-play
interactions, with-me-ness (for assessment of co-engagment).

carefully framed: as far as possible, they necessitate only the cognitive
capabilities that they evidence (e.g. if they evidence a purely socio-linguistic
mechanism, they will not mandate complex action capabilities – they may benefit
from it, though),

This point is especially important as it allows an incremental path: a robot
should be able to tackle one or several of these task independently of the
others, and a research team may progressively extend their cognitive models to
incorporate more and more of the cognitive capabilities required by the robot to
address all of the tasks.

@@

\paragraph{Child-Robot Interaction}
\label{ssec|CRI}
This free-play sandbox provides the opportunity to explore child-robot
interactions in this open-real world environment as shown in Figure
\ref{fig|freeplay}.

@@

\section{Task Implementation}
\label{sec:impl}

The sandbox is implemented using mainly two frameworks: Qt's QML and
\emph{QtQuick}\footnote{\url{http://doc.qt.io/qt-5/qmlapplications.html}}
for the graphical interface of the game, and the \emph{Robot Operating System}
(ROS) for the modular implementation of the data processing and behaviour
generation pipelines. The graphical interface interacts with the decisional
pipeline over a bidirectional QML-ROS bridge that we have developed for that
purpose\footnote{Source code: \texttt{[hidden for blind review]}}.

@@

\subsection{Interactive game} The interactive game
(Fig.~\ref{fig|architecture}.1) is coded using QML, and displays a main
background image on top of which items (animals, humans and objects) can be
moved.  The children can also use a drawing mode to create coloured strokes on a
layer between the background and the items, which adds another layer of
unconstrained interaction to the game (eg. Figure~\ref{fig|sandbox}. The game
exposes the image of the background, the drawings, and the positions of the
objects as a TF frame.

\subsection{Sensors} Two RGB-D cameras are mounted at fixed positions on the
Sandtray frame, each facing a child. This fixed position of the cameras allows
the extraction of social features such as head pose, eye gaze, pointing and body
posture, all described in a general coordinate system available to each software
node. In addition to the image, the cameras posses a microphone to record the
auditory aspect of the interaction. One node per camera
(Fig.~\ref{fig|architecture}.2) outputs on dedicated topics the audio and video
streams.

\todo{briefly present ROS pipeline for sensors}

@@

\paragraph{Wizard-of-Oz} To allow an experimenter to control the robot, a GUI to
control the robot (Fig.~\ref{fig|architecture}.11) is provided and presents an
identical representation of the state of the game on an other application which
can be used on a tablet for example. The wizard can drag the objects in a
similar fashion as what the child would do on the Sandtray, and on the release,
the robot executes the dragging motion on the Sandtray, moving an object to a
new location. The source code can easily modify to add new specific buttons to
execute other actions, such as having the robot talk to the child.

\todo{Should I add more in the WoZ GUI in the code side? It's fairly simple in the
current implementation}

@@

A web interface (Fig.~\ref{fig|architecture}.10) can be used by the experimenter
to manage the meta parameters of the interaction: log data on the subjects,
start-stop, select a task, manage data recording...

@@

Online processing can be done on the images obtained from the camera. Using new
deep learning libraries such as CMU's OpenPose~\cite{cao2017realtime} and
DLib~(ADDREF), posture and facial landmarks can be obtained online. As the
position of the camera, a potential robot and any object on the game is known,
this landmarks can be mapped to high level behaviours such as poiting or looking
at an object. Additional analysis can be done on the facial landmarks to other
social states, such as main emotion felt by the child.

@@

\todo{check section title}

Game features are also produced by the different nodes involved in the analaysis
of the game. The Playground segmentation produce a map of the regions based on
the colour which can be used with the positions of the animal to identify from
which zone to which zone an animal has been moved. The relative position of
animal can also indicate if two animals have been moved closer. These relations
and the drawing inform on what high level action the child is doing and can be
used to infer the child's goal or desire.

@@

A detailed description of the dataset is outside of the scope of this paper, and
we only provide hereafter cursory informations on the dataset. Specific details
regarding the methodology and the acquisition procedure can be found on the
dataset website: \url{https://freeplay-sandbox.github.io/}. The dataset is open and accessible
to any interested researcher.
\todo{Probably add "an anonymised version of the dataser is open..." Reviewers might be concerned about ethics}

@@

\todo{Check paragrap}
Figure \ref{fig|durations} presents an histogram of the durations of the
interactions for the two conditions. In the child-child condition, we can
observe two peaks, one around 10 to 15 minutes and one at 40 minutes, the
maximum allowed by the protocol. This indicates that the task is engaging for
the children and encourage them to play with each other for a consequent amount
of time and provides opportunities to display the social behaviours we aimed to
observe with it. In the child-robot condition, the peak at 40 minutes does not
appear (3 children play alongside the robot until the end of the time
allocated). The non-social robot appears to be less engaging than another child
but still elicit plays of an average duration of 19.2 minutes which both is
long enough to display social behaviours, and leaves us space for improvements
if the robot policy is more social.

>>>>

Capturing all the interactions taking place during the play sessions is possible
and practical with this setup. Even though the children will typically move a
little, the task is fundamentally a face-to-face, spatially delimited,
interaction, and as such simplifies the data collection. For instance, during
our dataset acquisition campaign (120 children, more than 45h of footage), the
children's faces were automatically detected in 98\% of the recorded frames (see
Section~\ref{sec:dataset}).

@@

%\paragraph{Socio-cognitive framing of the task}
%
%\todo{Very much unfinished section.}
%focus on abstract socio-cognitive facets (robot
%perception and manipulation are simplified); well suited for qualitative and
%quantitative analysis using metrics like Słowinski’s Individual Motor Signature
%(for behavioural alignment), Anderson's~\cite{anderson2004social} coding of children’s free-play
%interactions, with-me-ness (for assessment of co-engagment).
%
%carefully framed: as far as possible, they necessitate only the cognitive
%capabilities that they evidence (e.g. if they evidence a purely socio-linguistic
%mechanism, they will not mandate complex action capabilities – they may benefit
%from it, though),
%
%This point is especially important as it allows an incremental path: a robot
%should be able to tackle one or several of these task independently of the
%others, and a research team may progressively extend their cognitive models to
%incorporate more and more of the cognitive capabilities required by the robot to
%address all of the tasks.

@@

\paragraph{Child-Robot Interaction}
\label{ssec|CRI}

This free-play sandbox provides the opportunity to explore child-robot
interactions in this open, real world environment as shown in Figure
\ref{fig|freeplay}.

@@

\section{Implementation}
\label{sec:impl}

The software-side of the free-play sandbox is entirely
open-source\footnote{Source code: \texttt{[hidden for blind review]}}. It is
implemented using two main frameworks: Qt
QML\footnote{\url{http://doc.qt.io/qt-5/qmlapplications.html}} for the graphical
interface of the game, and the \emph{Robot Operating System} (ROS) for the
modular implementation of the data processing and behaviour generation
pipelines. The graphical interface interacts with the decisional pipeline over a
bidirectional QML-ROS bridge that we have developed for that purpose.

@@

\subsection{Interactive game} The interactive game
(Fig.~\ref{fig|architecture}.1) is coded using QML, and displays a main
background image on top of which items (animals, humans and objects) can be
moved. The children can also use a drawing mode to create coloured strokes on a
layer between the background and the items, which adds another layer of
unconstrained interaction to the game (Figure~\ref{fig|sandbox}). The game
exposes the image of the background, the drawings, and the positions of the
objects as ROS TF frames.

\subsection{Sensing} Two Intel RealSense SR300 RGB-D cameras are mounted at
fixed positions on the sandtray frame, with custom designed 3D-printed brackets
that ensure that the cameras are oriented towards the children's face. Because
the cameras are rigidly mounted onto the sandtray's frame, their accurate
geometric transformations with respect to the sandtray screen are known.
Combined with hardware calibration, it allows for accurate localisation of the
children and in particular, children's faces. In addition to the images, both
cameras can perform stereo audio recording. One ROS node per camera
(Fig.~\ref{fig|architecture}.2) publishes on dedicated topics the audio and video streams.

A third `external' (and non-calibrated) camera is usually used as well to record
the environment of the experiment with a wider angle (\emph{environment camera}
in Figure~\ref{fig|freeplay}).

@@

\paragraph{Wizard-of-Oz} To allow an experimenter to control the robot, a GUI to
control the robot (Fig.~\ref{fig|architecture}.11) is provided and presents an
identical representation of the state of the game on an other application which
can be used on a tablet for example. The wizard can drag the objects in a
similar fashion as what the child would do on the Sandtray, and on the release,
the robot executes the dragging motion on the Sandtray, moving an object to a
new location. The source code can be easily modified to add new specific buttons to
execute other actions, such as having the robot talk to the child.

%\todo{Should I add more in the WoZ GUI in the code side? It's fairly simple in the
%current implementation}

@@

We have developed as well a dedicated, web-based, interface can be used by the experimenter
to manage the whole experiment and data acquisition procedure
(Fig.~\ref{fig|architecture}.10). This interface ensures that all the required
software nodes are running, allow the experimenter to check the status and, if
needed, to start/stop/restart any of them. It also help managing large data
collection campaigns by providing a convenient web interface (usually used by
the experimenter on a tablet) to record the demographics, resetting the game
interface after each session, and automatically enforcing the acquisition
protocol (see Table~\ref{tab|protocol}).

This interface has been extensively used to acquire the dataset that we present at
Section~\ref{sec:dataset}.

@@

Off-line post-processing can be done on the images obtained from the cameras. We
rely on the CMU OpenPose library~\cite{cao2017realtime} to extract for both
children the upper-body skeleton, 70 facial landmarks including the pupil
position, as well as the hands' skeleton (when visible).

Further processing is possible: As the position of the
camera, a potential robot and any object on the game is known, this landmarks
can be mapped to high level behaviours such as pointing or looking at an object.
Additional analysis can be done on the facial landmarks to other social states,
such as main emotion felt by the child.

@@

Game features are also produced by the different nodes involved in the analysis
of the game. The Playground segmentation produce a map of the regions based on
the colour which can be used with the positions of the animal to identify from
which zone to which zone an animal has been moved. The relative position of
animal can also indicate if two animals have been moved closer. These relations
and the drawing inform on what high level action the child is doing and can be
used to infer the child's goal or desire.

@@

A detailed description of the dataset is outside of the scope of this paper, and
we only provide hereafter cursory informations on the dataset. Specific details
regarding the methodology and the acquisition procedure can be found on the
dataset website\footnote{\url{https://freeplay-sandbox.github.io/}}. The dataset is open
and accessible to any interested researcher, subject to adequate ethical clearance.

@@

Figure~\ref{fig|durations} presents an histogram of the durations of the
interactions for the two baselines. The distribution of the child-child
interaction durations shows that (1) all children
engage easily and for non-trivial amounts of time with the task; (2) the task
leads to a wide range of level of commitment, which is desirable: it supports
the claim that the free-play sandbox is an effective paradigm to observe a range
of different social behaviours; (3) long interactions (>30 min) can result,
which is especially desirable to study social dynamics.

In contrast, and notwithstanding the smaller number of participants, the
distribution of the child-robot interaction durations shows these interactions are
generally shorter. This is expected as the robot was explicitly programmed not
to interact with the children, resulting in a rather boring (and at time,
awkward) situation where the child and the robot where playing side-by-side --
in some case for rather long periods of time -- without interacting at all.
